Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-08-31 main/doc/chord_sysprops.tex
documentation changes

\item
\code{chord.src.path} \\
{\bf Type:} path \\
{\bf Description:} Java source path of the given program. \\
{\bf Default value:} {\tt ""}  \\
{\bf Note:} \Chord\ analyzes only Java bytecode, not Java source code.  This property is used only by the task of converting Java source files into HTML files by program analyses that need to present their analysis results at the Java source code level (by calling method \code{chord.program.Program.getProgram().HTMLizeJavaSrcFiles())}.

@@

\begin{itemize}
\item
\code{chord.build.scope} \\
{\bf Type:} bool \\
{\bf Description:} Compute the scope (i.e., reachable classes and methods) of the given program using the algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} The program scope is computed regardless of the value of this property if another task (e.g., a program analysis specified via property \code{chord.run.analyses}) demands it by calling method \code{chord.program.Program.getProgram()}.

@@

\begin{itemize}
\item
\code{chord.verbose} \\
{\bf Type:} bool \\
{\bf Description:} Produce more verbose output during \Chord's execution. \\
{\bf Default value:} {\tt false}

\item
\code{chord.bddbddb.noisy} \\
{\bf Type:} bool \\
{\bf Description:} Produce more verbose output during the Datalog solver \bddbddb's execution. \\
{\bf Default value:} {\tt false}

>>>>

\item
\code{chord.src.path} \\
{\bf Type:} path \\
{\bf Description:} Java source path of the given program. \\
{\bf Default value:} {\tt ""}  \\
{\bf Note:} \Chord\ analyzes only Java bytecode, not Java source code.  This property is used only by the task of converting Java source files into HTML files by program analyses that need to present their analysis results at the Java source code level (by calling method \code{chord.program.Program.g().HTMLizeJavaSrcFiles())}.

@@

\begin{itemize}
\item
\code{chord.build.scope} \\
{\bf Type:} bool \\
{\bf Description:} Compute the scope (i.e., reachable classes and methods) of the given program using the algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} The program scope is computed regardless of the value of this property if another task (e.g., a program analysis specified via property \code{chord.run.analyses}) demands it by calling method \code{chord.program.Program.g()}.

@@

\begin{itemize}
\item
\code{chord.verbose} \\
{\bf Type:} int in the range [0..3] \\
{\bf Description:} Control the verbosity of logging during \Chord's execution. \\
{\bf Default value:} {\tt 2}

\item
\code{chord.bddbddb.verbose} \\
{\bf Type:} int in the range [0..5] \\
{\bf Description:} Control the verbosity of logging during the execution of JavaBDD (BDD library) and \bddbddb\ (Datalog solver). \\
{\bf Default value:} {\tt 0}
